Dear Prof. Morii,

I am writing you to apply for the Post-doctoral position in the ATLAS Harvard group.
I am currently a PhD student at the Institut de Física d'Altes Energies (IFAE),
Barcelona (Spain), working on searches for new physics in top-like final states at
the ATLAS experiment. My thesis will cover three publication results and a preliminary
result, in all of which I have been a primary author, and I currently plan to defend
it in Janurary 2014.

During my PhD I have performed studies on the single pion response in the Tilecal
calorimeter and performed searches for new heavy quarks, first with an analysis
focused on signals from fourth generation chiral quarks and more recently
on vector-like top quark partners. The final states I have investigated are actually
common to many other new physics scenarios, including Supersymmetry. During my
postdoctoral appointment I would be interested to continue working on searches
for physics beyond the standard model, as the new energy and luminosity frontier
at the LHC Run 2 will bring many opportunities for discovery, where I hope my PhD
experience will prove quite valuable.

At the same time, I am open to new physics projects, including Standard Model
measurements that will stress test our understanding of main backgrounds to new
physics searches, as well as measurements of Higgs properties that are critical to
unravel the nature of the discovered Higgs-like particle.

The ATLAS Harvard group has a long-standing track record for the quality of its
research, and is well positioned in the above physics topics, which make this
opening particularly attractive to me.

In addition to physics analysis, I consider hardware experience a must for a
well-rounded experimental physicist. Therefore, I am eager to take part in the
ATLAS upgrade effort, in particular for what concerns the new small wheels testing
and characterization.

You may find in the attachment my CV, statement of research interests and
the list of publications. I have arranged recommendation letters to be sent by:

Prof. Aurelio Juste (ICREA/IFAE)
Prof. Erez Etzion (Tel Aviv University)
Prof. Ana Henriques (CERN)

I very much hope you will consider positively my application and look forward
to hearing from you.

Sincerely,

Antonella Succurro








Dear Angela,

I am writing to apply for the Post-doctoral position in the ATLAS Harvard group.
I am currently a PhD student at the Institut de Física d'Altes Energies (IFAE)
working on searches for new physics in top-like channels at the ATLAS experiment.
I plan to defend my thesis in January 2014.

During my PhD I have performed searches for new heavy quarks, first with an analysis
focused on signals from fourth generation chiral quarks and more recently
on vector-like top partners. The final states we 
have investigated are actually common to many possible new physics objects, including
Supersymmetric particles. I would like to keep working on searches for physics 
beyond the standard model focusing on singly produced vector-like quarks but I am
also willing to enrich my experience by joining other projects.

On top of physics analysis I would like to take part in the ATLAS upgrade
effort, in particular for what concerns the new small wheels testing
and characterization.

You may find in the attachment my CV, statement of research interests and the list
of publications.

I have arranged recommendation letters to be sent by:
Dr. Aurelio Juste (IFAE)
Prof. Erez Etzion (Tel Aviv University)
Dr. Ana Henriques (CERN)

I look forward to hearing from you.  
Sincerely,
Antonella Succurro
