
\roottitle{Research Activity}


\headedsection{\textsc{Systems Biology}}{May 2014 - present} {

\vspace*{.3cm}

\headedsubsection{\href{http://ceplas.eu/en/}{\color{myblue} CEPLAS}}{University of Cologne (Germany), }{\footnotesize Sep 2016 - present} 

{\bodytext{\small
The Cluster of Excellence on Plant Science brings together researchers from different institutions and with different
expertises to address current challenges in the study of plant science. Here I am studying microbial communities associated
to plant roots using novel approaches that bridge bioinformatics data analysis with metabolic modeling to understand the driving
mechanisms in the establishing of symbiosis in the rhizosphere. For this I work in very close collaboration with experimentalists,
taking part in the experiment design.
}}

\headedsubsection{\color{gray} Achieved Skills}{\color{gray} Bioinformatics, Database Management}


\headedsubsection{\href{http://www.accliphot.eu/}{\color{myblue} AccliPhot}}{Heinrich Heine Universität Düsseldorf (Germany), }{\footnotesize Sep 2014 - Sep 2016} 

{\bodytext{\small
%How does the photosynthetic metabolic network in microalgae and plants adapt upon changes in external light conditions during short-time intervals?
%My main research project within the Environmental Acclimation of Photosynthesis (AccliPhot) Marie Curie ITN
%focuses on modeling the signaling pathways in plants and microalgae, in particular the key role of kinases and phosphatases enzymes. 
How do microalgae and plants adapt upon changes in environmental conditions? What are the effects on metabolism? How can we obtain 
stable cultures of microalgae at the industrial scale? Within the Environmental Acclimation of Photosynthesis (AccliPhot) Marie Curie ITN I
investigated how algae and bacteria exchange nutrients and cofactors in mutualistic consortia. By
extending the scope of dynamic FBA to include the effect of metabolite concentrations on reaction fluxes I aim at in silico discovery of
robust synthetic ecology communities for industrial cultures. I developed a novel multilevel modeling approach coupling ODE and dFBA
that integrates different levels of complexity.
}}


\headedsubsection{\color{gray} Achieved Skills}{\color{gray} R, dFBA, ODE, Teaching, Genetic Algorithms, Student Supervision, Wet Lab, Grant Proposals}

\headedsubsection{\href{http://timing-metabolism.eu/}{\color{myblue} TiMet}}{University of Aberdeen (UK), }{\footnotesize May - Sep 2014} 


{\bodytext{\small
The european TiMet project aims at achieving a better understanding of how plants regulate their metabolism in response to the alternation of day and night.
During a very short term appointment I have been involved in studying Flux Balance Analysis with the aim of applying it to microbial communities associated with growth of plants.
}}


\headedsubsection{\color{gray} Achieved Skills}{\color{gray} Biology, Flux Balance Analysis, Matlab, Biochemistry, Linear Programming}



}



\headedsection{\textsc{High energy particle physics}}{February 2010 - February 2014} {

\headedsubsection{\href{http://atlas.ch/}{\color{myblue} ATLAS experiment}}{{CERN (Switzerland) \& IFAE (Spain)}} 

{\bodytext{\small
Is our Standard Model (SM) of the fundamental particle interactions complete? Apparently, the answer is ``no''. Many theories have been proposed to explain what is currently not understood, like the nature of Dark Matter, or the reason why the Higgs boson is so light. With data from the Large Hadron Collider (LHC) at the CERN laboratory of Geneva, the ATLAS experiment can probe new physics. I worked on various analyses aimed at the discovery (or exclusion) of a signal from a new quark similar to the top quark but with a larger mass. The results were the first to propose a model-independent way for comprehensive searches of vector-like quarks.
 I was involved also in other projects, in particular I have contributed to various performance studies of the ATLAS Tile Hadronic Calorimeter and for several months I have been responsible for the optimization of data-driven techniques to estimate the contribution of multi-jet events in a particular search channel used by many analyses of the ATLAS collaboration.}}

\headedsubsection{\color{gray} Achieved Skills}{\color{gray} Monte Carlo techniques, Statistical Analysis, 
ROOT, C++, Python, Bash scripting, RCS, 
Team working, Scientific writing, Written and Oral presentation skills, 
TWiki documentation}

}

