


\roottitle{\textsc{Presentation}}
\headedsection{How I see myself now}{\small I enjoy facing new challenges where I can put my intelligence and expertise into work. I am enthusiastic in learning new things and do not like repetitive tasks. I always prefer to put a bit more effort into a smart, re-usable, flexible solution than achieve the desired result in the boring, straight way. I love when different disciplines merge together towards a common goal, it's a precious opportunity to increase one's knowledge in unfamiliar fields. I like to work in team and I value a lot others' opinion, but when more efficient I prefer to work on my own in my own way.}% I am a good listener and I am not afraid of constructive criticism.}
\headedsection{Objective}{\small Work in a highly motivating environment, further develop my problem solving skills.}
\headedsection{Experience and skills}{\small My experience developed inside the high energy physics research field and my curriculum is mainly academic. I worked for more than four years in a collaboration of 4000+ people in one of the most technologically advanced laboratories of the world. I faced many challenges and am not afraid of competition. I know how to coordinate tasks, how to present my results to general public or to experts in my field. I experienced that I can easily learn how to use new tools and computing languages in a short time.}
%\headedsection{How I see myself in a year from now}{\small Involved in a high qualified job, mastering new skills.}
