
\roottitle{Professional Experience}

\headedsection{\textsc{Postdoctoral CEPLAS Research Fellow}}{University of Cologne, Germany} {

\headedsubsection{\color{myblue}Sep~2016 - Oct~2017}{PI: Prof. Stanislav Kopriva}

}

\headedsection{\textsc{Postdoctoral Marie Curie Research Fellow}}{Heinrich Heine Universität Düsseldorf, Germany} {

\headedsubsection{\color{myblue}Sep~2014 - Sep~2016}{PI: Jun. Prof. Oliver Ebenhöh}

}

\headedsection{\textsc{CEPLAS associated postdoc}}{Cluster of Excellence on Plant Sciences, Düsseldorf, Germany} {

\headedsubsection{\color{myblue}Oct~2015 - Sep~2016}{PI: Jun. Prof. Oliver Ebenhöh}

}

\headedsection{\textsc{Visiting Scientist}}{Boston University, MA, USA} {

\headedsubsection{\color{myblue}Aug~-~Dec~2014}{PI: Prof. Daniel Segré}

}

%\headedsection{\textsc{University of Aberdeen}}{UK} {
\headedsection{\textsc{Postdoctoral Research Fellow}}{University of Aberdeen, UK} {

\headedsubsection{\color{myblue}May~-~Sep~2014}{PI: Dr. Oliver Ebenhöh}

}

%\headedsection{\textsc{Institut de Física d'Altes Energies \& Universitat Autònoma de Barcelona}}{Spain} {
\headedsection{\textsc{Doctoral Student}}{Institut de Física d'Altes Energies \& Universitat Autònoma de Barcelona, Spain} {

\headedsubsection{\color{myblue}Feb~2010 - Feb~2014}{PI: Prof. Aurelio Juste}

}

%\headedsection{\textsc{Institut de Física d'Altes Energies \& Universitat Autònoma de Barcelona}}{Spain} {
\headedsection{\textsc{Visiting Scientist}}{Centre Européen pour la Recherche Nucléaire (CERN), Switzerland} {

\headedsubsection{\color{myblue}Feb~2010 - Apr~2013}{PI: Prof. Aurelio Juste; PL: Dr. Fabiola Gianotti}

}

%\headedsection{\textsc{Istituto Nazionale di Fisica Nucleare (INFN) \& Università degli Studi di Pavia}}{Italy} {
\headedsection{\textsc{INFN associate}}{Istituto Nazionale di Fisica Nucleare (INFN) \& Università degli Studi di Pavia, Italy} {

\headedsubsection{\color{myblue}Jun~-~Dec~2009}{PI: Dr. Giacomo Polesello}

}

\headedsection{\textsc{Visiting Student}}{Université de Genève \& CERN, Switzerland} {

\headedsubsection{\color{myblue}Feb~-~Jun~2009}{PI: Prof. Allan Clark}

}

